\section{Conclusion}\label{sec:conclusion}
We have explored the possibility of improving news article search using various \gls{ir} method combinations.
The focus has been on testing whether using the \gls{lda} topic model could improve the performance of the article retrieval.

Based on the findings of this paper, we will now answer the questions posed in \autoref{sec:intro}:
\begin{quote}
	\begin{itemize}
		\item \emph{How can we generate queries for a dataset to use for \gls{ir}?}
		\item \emph{How can we evaluate \gls{ir} methods in a way that favors abstraction, rather than word frequency?}
		\item \emph{Can \gls{pr} be used on a document dataset with no explicit connections to improve \gls{ir} methods?}
	\end{itemize}
\end{quote}

For the first two questions, queries can be generated in different ways depending on what the purpose of the evaluation is.
We generate two types of queries based on either important words from a specific document or a specific topic.
We differentiate between these two query types to favor both the specificity of finding a specific document and the more abstract idea of finding documents related to a topic.
We have evaluated various \gls{ir} methods' \gls{ir} performance using these queries, measuring \acrlong{map}, P@n, and mean rank.
The results from \autoref{tab:results} and \autoref{tab:results_precision_at_10} indicate that, when searching for documents in a topic, combinations using \gls{lda}-\gls{ir} can perform better than \gls{bm25} when longer queries are used.
However, this does come at the cost of decreased performance in document query retrieval.

For the third question, we explored the possibility of creating the adjacency matrix for \gls{pr} by using the similarity between \gls{lda} topic distributions, generated for the articles.
This was as an alternative to explicit relations between documents, such as references between scientific articles.
The results in \autoref{tab:results}, \autoref{tab:results_precision_at_10}, and \autoref{tab:hit_results}, show this to have been highly effective, since most best performing \gls{ir} methods include \gls{pr}.
In addition, most of the tested \gls{ir} methods improve their performance when \gls{pr} is added as part of a combination.
